Transit time distributions.

### 2014-12-19 prep_figures/commute/access-distn.Rmd
Less bad names for access distribution stuff.

d <- rbind(
  grab_data("runs/run1-uniq_trees_T-col-CCC1_2D_3D_C4_5DD-CC1_C2_3DD_C4_5DD.tab"),
  grab_data("runs/run1-uniq_trees_T-col-CCCC1_2D_3D_4D_5D-CCCC1_2D_3D_5D_4D.tab"),
  grab_data("runs/run1-uniq_trees_T-col-CCCC1_2D_3D_4D_5D-CCC1_2D_3D_C4_5DD.tab"))

sub_d <- subset(d, t1 != t2)

ggplot(sub_d, aes(x=time, y=dens, color=cmp)) + geom_line() + scale_x_continuous(limits=c(0,100))
```

>>>>

data_of_num <- function(n) {
  df <- grab_data(paste0("runs5/run1.",as.character(n),".tab"))
  df$num <- as.factor(n)
  df
}

d <- do.call(rbind, lapply(c(7,14,66,68,69), data_of_num))

sub_d <- subset(d, t1 != t2)
sub_d <- subset(d, t1 < t2)

ggplot(sub_d, aes(x=time, y=dens, color=num)) + geom_line() + scale_x_continuous(limits=c(0,25))
```
